\documentclass{article}

\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{enumitem}

\usepackage[backend=biber, style=numeric-comp]{biblatex}
\addbibresource{tex/biber.bib}

\geometry{left=4.5cm,top=2cm,bottom=2cm,right=4.5cm}

\hypersetup{colorlinks=false,
	linkcolor=black,
	filecolor=black,
	urlcolor=black,
	bookmarks=true
}

\urlstyle{mono}

\newcommand{\program}{Imago}

\newcommand{\fref}[1]{Fig.~\ref{#1}}
%\newcommand{\uurl}[1]{\underline{\url{#1}}}

\begin{document}

\frenchspacing

\title{\program: An AI capable of playing the game of Go}

\author{Íñigo Gutiérrez Fernández}

\date{}

\maketitle

\begin{abstract}
	This is the abstract.
\end{abstract}

\clearpage

\section*{Acknowledgements}

TODO: Acknowledgements

To Vicente García Díaz, for directing me in this project.

To José Manuel Redondo López\cite{plantillaRedondo}, for making a very
complete template on which the structure of this documentation is extensively
based.

\clearpage

\section*{Copyright notice}

\begin{displayquote}

	Copyright (C) 2021 \textbf{ÍÑIGO GUTIÉRREZ FERNÁNDEZ}.

	\textit{Permission is granted to copy, distribute and/or modify this
	document under the terms of the GNU Free Documentation License, Version 1.3
	or any later version published by the Free Software Foundation; with the
	Copyright notice as an Invariant Section, no Front- Cover Texts, and no
	Back-Cover Texts.  A copy of  the license  is  included in  the  section
	entitled ``GNU Free Documentation License''.}

\end{displayquote}

Although this document uses the GNU Free Documentation License to keep its
contained information free, bear in mind that it isn't software documentation or
a manual or guide of any kind, and serves just as the documentation for the
author's Degree's Final Project.

This document is based on a template by José Manuel Redondo López, associate
professor of the University of Oviedo. The copyright notice he asks for
inclusion to use this template is included here.

\begin{displayquote}

	Copyright (C) 2019 \textbf{JOSÉ MANUEL REDONDO LÓPEZ}.\cite{plantillaRedondo}

	\textit{Permission is granted to copy, distribute and/or modify this
	document under the terms of the GNU Free Documentation License, Version 1.3
	or any later version published by the Free Software Foundation; with no
	Invariant Sections, no Front- Cover Texts, and no Back-Cover Texts.  A  copy
	of  the license  is  included in  the  section entitled ``GNU  Free
	Documentation License''.}

\end{displayquote}

\clearpage

\tableofcontents

\input{tex/introduction.tex}

\input{tex/planification.tex}

\input{tex/systemAnalysis.tex}

%\input{tex/interface.tex}

%\input{tex/implementation.tex}

\printbibliography{}

\end{document}
